Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars

### 2018-08-24 main.tex
reference update. typos.

Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gas-rich, star forming, low-mass dwarf galaxy, with an observable HII region, necessary for determining gas phase abundances, that is close enough to the Milky Way to conduct this experiment. Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}. As discussed in Section~\ref{sec:chemical evolution}, more than 90\% of the tracked metals produced during our simulation no longer reside within the galaxy's disk, agreeing with observations. However, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs. Although more than half of these metals are expected to eventually re-accrete \citep{Angles-Alcazar2017}, it is still possible that most of the metals that have been produced at these early times will remain outside the galaxy disk.

@@

\setcounter{figure}{0}
\section{H$^{-}$ Photodetachment}
\label{appendix:H minus}
%\textbf{This section is new:}

\textbf{As discussed in Section~\ref{sec:molecular gas content}, H$_2$ formation is dominated by the gas-phase H$^{-}$ channel in our simulations. Accounting for the photodetachment of H$^{-}$ from the stellar radiation field, which may dominate over the UVB, 
%mm ca 
    can 
be important for correctly modeling H$_2$ formation in low metallicity gas~\citep{Wolcott-Green2012}. To test the significance of this radiation in determining the final H$_2$ mass we run a grid of one-zone Grackle cooling models.\footnote{See the ``cooling\_cell.py'' example here for more details: https:\/\/grackle.readthedocs.io\/en\/grackle-3.1\/Python.html}  These runs iterate through the non-equillibrium chemistry and cooling solvers with a constant density (10~cm$^{-3}$) for 200~Myr. In Fig.~\ref{fig:Grackle grid} we plot the final H$_2$ mass fraction in these cells for variations over five orders of magnitude in the adopted H$^{-}$ photodetachment rate and the Lyman-Werner radiation background. As shown, the H$_2$ mass fraction is much more sensitive to the Lyman-Werner radiation field than the H$^-$ photodetachment rate. In effect, our simulations move left-to-right in this diagram (only) as stars form (right) or die (left). A complete model, including the stellar contribution to H$^{-}$ photodetachment, would move somewhat diagonally.}

\textbf{We follow up on the qualitative conclusions of these models by running four full-physics simulations, but with no star formation, at the four points starred in the diagram. These vary the radiation bands by factors of 100 each, which is comparable to the ratio between the typical ISRF and the UVB in the disk of our galaxy (see Fig.~\ref{fig:ISRF}). Changing the background H$^{-}$ photodetachment rate by a factor of 100 only (top left star) leads to a reduction in the final H$_2$ mass fraction by 3, while changing the Lyman-Werner background by a factor of 100 (bottom right point) decreases the H$_2$ mass by a factor of 6.9. Applying both scale factors gives a reduction of 7.9.}

@@

\textbf{H$^-$ photodetachment arises from lower energy photons, above 0.76~eV, with a peak in effectiveness around 2~eV. For this reason, low mass stars may contribute significantly, if not dominate, the radiation field responsible for this reaction. Although we demonstrate that the H$_2$ fraction is more sensitive to the Lyman-Werner radiation field in our simulations, this radiation is dominated by short-lived massive stars and thus subject to fluctuations. Particularly in periods of no star formation, the regulation of H$^-$ photodetachment from low energy photons may play a non-negligible role in regulating H$_2$ formation. Indeed there is H$_2$ growth during these periods due to a decrease in the Lyman-Werner field, but it is unclear how much of this would be attenuated by accounting for photons from lower mass stars. Doing so in our current model, applying an optically thin $1/R^2$ field for each star, would be computationally challenging due to the dramatic increase in the number of stars whose radiation would need to be tracked. }

>>>>

Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gas-rich, star forming, low-mass dwarf galaxy, with an observable HII region, necessary for determining gas phase abundances, that is close enough to the Milky Way to conduct this experiment. Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}. As discussed in Section~\ref{sec:chemical evolution}, more than 90\% of the tracked metals produced during our simulation no longer reside within the galaxy's disk, agreeing with observations. However, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs. Although more than half of these metals are expected to eventually re-accrete \citep{Christensen2016,Angles-Alcazar2017}, it is still possible that most of the metals that have been produced at these early times will remain outside the galaxy disk.

@@

\setcounter{figure}{0}
\section{H$^{-}$ Photodetachment}
\label{appendix:H minus}

\textbf{As discussed in Section~\ref{sec:molecular gas content}, H$_2$ formation is dominated by the gas-phase H$^{-}$ channel in our simulations. Accounting for the photodetachment of H$^{-}$ from the stellar radiation field, which may dominate over the UVB, can be important for correctly modeling H$_2$ formation in low metallicity gas~\citep{Wolcott-Green2012}. Our current model does not include this contribution. To test the significance of this radiation in determining the final H$_2$ mass we run a grid of one-zone Grackle cooling models.\footnote{See the ``cooling\_cell.py'' example here for more details: https://grackle.readthedocs.io/en/latest/Python.html}  These runs iterate through the non-equillibrium chemistry and cooling solvers with a constant density (10~cm$^{-3}$) and initial temperature of 10$^{4}$~K for 200~Myr. In Fig.~\ref{fig:Grackle grid} we plot the final H$_2$ mass fraction in these cells for variations over five orders of magnitude in the adopted H$^{-}$ photodetachment rate and the Lyman-Werner radiation background. As shown, the H$_2$ mass fraction is much more sensitive to the Lyman-Werner radiation field than the H$^-$ photodetachment rate. In effect, our simulations move left-to-right in this diagram (only) as stars form (right) or die (left). A complete model, including the stellar contribution to H$^{-}$ photodetachment, would move somewhat diagonally.}

\textbf{We follow up on the qualitative conclusions of these models by running four full-physics simulations, but with no star formation, at the four points starred in the diagram. These vary the radiation bands by factors of 100 each, which is comparable to the ratio between the typical ISRF and the UVB in the disk of our galaxy (see Fig.~\ref{fig:ISRF}). Changing the background H$^{-}$ photodetachment rate by a factor of 100 only (top left star) leads to a reduction in the final H$_2$ mass fraction by 3, while changing the Lyman-Werner background by a factor of 100 (bottom right point) decreases the H$_2$ mass by a factor of 6.9. Applying both scale factors gives a reduction of 7.9. Thus, we see that the difference between the more realistic case in which both rates increase by the same factor, and the case assumed in the simulations, is only about 20\%.}

@@

\textbf{H$^-$ photodetachment arises from lower energy photons, above 0.76~eV, with a peak in effectiveness around 2~eV. For this reason, low mass stars may contribute significantly, if not dominate, the radiation field responsible for this reaction. The Lyman-Werner radiation field is dominated by short-lived massive stars, with some contribution from older stars up to a few hundred Myr, and is thus subject to significant fluctuations, particularly in periods of no star formation. During these times, H$^-$ photodetachment from low energy photons may play a non-negligible role in regulating H$_2$ formation. Indeed there is H$_2$ growth during these periods due to a decrease in the Lyman-Werner field, but it is unclear how much of this would be attenuated by accounting for photons from lower mass stars. Doing so in our current model, applying an optically thin $1/R^2$ field for each star, would be computationally challenging due to the dramatic increase in the number of stars whose radiation would need to be tracked.}

\textbf{As emphasized in Section~\ref{sec:molecular gas content}, further work modeling low-metallicity dwarf galaxies with a more detailed chemistry model would be useful to clarify the role of various competing phenomena in driving the molecular properties of these galaxies.}
